Bootstrapping Multi-atlas Hippocampal Segmentation with MAGeT

### 2013-03-01 paper.Rnw
Winterburn atlas figure

>>>>

<<WAval-boxplot,cache=T>>=
# dirty dirty
data = read.csv('data/WAval.csv')
orig = subset(data, version == "orig")
voted = subset(data, version == "voted")
origtotal = orig[,2:6] + orig[,7:11]
votedtotal = voted[,2:6] + voted[,7:11]
pchange = abs((origtotal - votedtotal)/origtotal)
diff = cbind(orig[,1],pchange)

melted = melt(diff, id.vars="orig[, 1]")
names(melted) <- c("subject","variable","value")
ggplot(melted, aes(y=value,x=variable,colour=subject,group=subject)) + 
  geom_point(size=3) + 
  geom_lin() + 
  labs(title="Percent difference in MAGeT volumes from original",
       y="Percent difference in volume") 
@
